Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-10-05 supplement/06_bat_data.Rmd
minor updates to text

![A visual examination of plots of the bats' residence patches and linear approximations of paths between them showed that though all three bats roosted at the same site, they used distinct areas of the study site over the three nights **(a)**.
Bats tended to be resident near fruit trees, which are their main food source, travelling repeatedly between previously visited areas **(b, c)**.
However, bats also appeared to spend some time at locations where no fruit trees were recorded, prompting questions about their use of other food sources **(b, c)**.
When bats did occur close together, their residence patches barely overlapped, and their paths to and from the broad area of co-occurrence were not similar **(c)**.
Constructing residence patches for multiple individuals over multiple activity periods suggests interesting dynamics of within- and between-individual overlap **(b, c)**.](../figures/fig_08.png)

>>>>

## Main text Figure 8

See Fig. 8 in the main text, made with QGIS.

![A visual examination of plots of the bats' residence patches and linear approximations of paths between them showed that though all three bats roosted at the same site, they used distinct areas of the study site over the three nights **(a)**.
Bats tended to be resident near fruit trees, which are their main food source, travelling repeatedly between previously visited areas **(b, c)**.
However, bats also appeared to spend some time at locations where no fruit trees were recorded, prompting questions about their use of other food sources **(b, c)**.
When bats did occur close together, their residence patches barely overlapped, and their paths to and from the broad area of co-occurrence were not similar **(c)**.
Constructing residence patches for multiple individuals over multiple activity periods suggests interesting dynamics of within- and between-individual overlap **(b, c)**.](figures/fig_08.png)
